Development of a permanent magnet characterisation framework for use in low-field MRI systems

### 2024-02-27 documentation/colloquium/presentation/index.qmd
.

@@

![](images/3D_sensor.png)

@@

* data aqusition using hardware sensors
* data storage
* data analysis tasks

@@

@@

@@

@@

@@

<table>
<tr><td><p>[<img src="images/github-mark-white.png" alt="image" width="150" height="auto">](https://github.com/LFB-MRI/MagneticReadoutProcessing) </p></td><td><p>[<img src="images/researchgate.svg" alt="image" width="150" height="auto">](https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterisation_framework_for_use_in_low-field_MRI_systems) </p><td>[<img src="images/avatar.png" alt="image" width="150" height="auto">](https://marcelochsendorf.com)</td></td></tr>
</table>

>>>>

<aside class="notes">
    *
    Folgend ein paar beispiele
</aside>

@@

::: {.container}
:::: {.col}
<h4 style="text-align: center;">3D Rotational Sensor</h4>
::::
:::

::: {.container}
:::: {.col}
<img src="images/3D_sensor.png" alt="image" height="320px">
::::

:::: {.col}
<img src="images/3D_sensor_measurement.png" alt="image" height="320px" >
::::
:::

::: {.container}
:::: {.col}
<h4 style="text-align: center;">1D Static Sensor</h4>
::::
:::

::: {.container}
:::: {.col}
<img src="images/1D_sensor.png" alt="image" height="320px">
::::

:::: {.col}
<img src="images/1D_sensor_measurement.png" alt="image" height="320px" >
::::
:::

@@

*
* data aqusition
* data storage
* data analysis tasks

@@

![](images/Sensor_evaluation_setup_for_linearity_measurements.png)

@@

### *MM5603NJ* chraterisation results

@@

* Generate automated measurement using hardware sensors
* Save results to filesystem for later analysation

@@

* Execution of pre-configured analysation and pipeline
* User implements filter algorithm only

@@

<table>
<tr><td><p>[<img src="images/github-mark-white.png" alt="image" width="150" height="auto">](https://github.com/LFB-MRI/MagneticReadoutProcessing) </p></td><td><p>[<img src="images/researchgate.svg" alt="image" width="150" height="auto">](https://www.researchgate.net/publication/374388764_Development_of_a_permanent_magnet_characterisation_framework_for_use_in_low-field_MRI_systems) </p><td>[<img src="images/avatar.png" alt="image" width="150" height="auto">](https://marcelochsendorf.com)</td><td><p>[<img src="images/pypi.svg" alt="image" width="150" height="auto">](https://pypi.org/project/MagneticReadoutProcessing/) </p></td><td><p>[<img src="images/rtd.png" alt="image" width="150" height="auto">](https://magneticreadoutprocessing.readthedocs.io/en/latest/) </p></td></tr>
</table>
